The Rockerverse: Packages and Applications for Containerisation with R

### 2020-06-11 README.Rmd
add HTML link of arXiv paper to README

Article about everything related to containers and R, originally based on [this blog post](http://bit.ly/docker-r) and now **available as a preprint on arXiv.org: https://arxiv.org/abs/2001.10641**.

>>>>

Article about everything related to containers and R, originally based on [this blog post](http://bit.ly/docker-r) and now **available as a preprint on arXiv.org: https://arxiv.org/abs/2001.10641** ([read as HTML](https://www.arxiv-vanity.com/papers/2001.10641/)).
